\documentclass{article}
\usepackage[utf8]{inputenc}
\begin{document}
\begin{center}    
{\huge Minutes of the Third Group Meeting \par}
\vspace{0.5cm}
{\large Group UG02 \par}
\vspace{0.5cm}
{\large Monday 7th August 2017 \par}
\vspace{0.5cm}
\end{center}

\begin{flushleft}
\begin{tabular}{ll}
{\bfseries Chair} & Alexander Good \\
{\bfseries Minutes} & Andrew Graham \\
{\bfseries Members} & Nathan Crowe \\
 & Brock Campbell \\
 & Mitchell Mickan \\
 & Saxon Nelson-Milton \\
 & Jiashi (Josh) Song \\
{\bfseries Apologies} & None\\
\end{tabular}
\end{flushleft}

\section{Time and Place}
The {\itshape second} meeting in {\itshape week 4} for the Software Engineering Group Project Group was held in the {\bfseries Atrium of Ingkarni Wardli}, at {\bfseries 2:05am on Monday 14th August 2017.} 

\section{Issues and Actions}
	\subsection{Requirements Grouping}
		\subsubsection*{Issue}
		We have a large list of requirements that need to be grouped into subsections, also the importance of the requirements needs to be set based on the dependencies between the requirements.
    	\subsubsection*{Action}
    	Requirements were discussed and grouped into different sections.  These included the rover requirements, mapping, missiong, design and uncategorized requirements. The requirements map provided by Mitchell was referred to as a guide for working out dependencies. It was determined that an initial goal would be to get the rover moving adequately before doing detection handling.
     \subsection{Physical Design}
		\subsubsection*{Issue}
		Since we now have access to the rover kit, we are able to start designing the rover. It was highlighted that the physical design would be an important factor in the final success of our rover.
    	\subsubsection*{Action}
    	It was decided to go to the lab directly after the meeting and work on a prototype design that could be presented in the client meeting. This was completed and a prototype design is ready to present.

\section{Client Meeting Preparation}
\subsection{Overall Preparation}
Group discussed questions posed in agenda for tomorrows meeting, prioritized each of them and organized them into categories.
\subsection{Individual Preparation}
According to the forum post, it was decided that each person should introduce themselves in the meeting and prepare a short statement that outlined their role and shadow role within the group. 
The statement could include work already completed pertaining to the manager's role and also the work that would be completed in the future.
\subsection{Robot Naming}
The group decided on Ava 2.0 or Ava as our robot name, based on the movie Ex Machina.
\section{Adjournment}
	The next group meeting and will be held in the {\bf Atrium, Ingkarni Wardli} at {\bf 2:00pm on Monday 20th August 2017}.\newline
    The next client meeting and will be held in {\bf Room 462, Ingkarni Wardli} at {\bf 10:10am on Tuesday 14th August 2017}.\newline
The meeting closed at 3:05pm.
\end{document}
