\documentclass[11pt, a4paper]{article}

%\usepackage[ampersand]{easylist}

\begin{document}

\begin{center}    
{\huge Meeting Minutes Week 2 \par}
\vspace{0.5cm}
{\large Group UG02 \par}
\vspace{0.5cm}
{\large 04/08/2017 \par}
\vspace{0.5cm}
\end{center}

\begin{flushleft}
\begin{tabular}{ll}
{\bfseries Chair} & Brock Campbell \\
{\bfseries Secretary} & Nathan Crowe \\
 & Alexander Good \\
 & Andrew Graham \\
 & Mitchell Mickan \\
 & Saxon Nelson-Milton \\
{\bfseries Apologies} & None\\
\end{tabular}
\end{flushleft}

\section{Time and Place}
	The {\itshape first} meeting in {\itshape week 2} for the Software Engineering Group Project Group UG02 was held at the {\bfseries Ingkarni Wardli atrium}, at {\bfseries 2:00pm on Monday 31 July 2017.} 
	
\section{Quorum Announcement}
	The Chairman announced that a quorum of the group was present, and that the meeting, having been duly convened, was ready to proceed with its business.	
	
\section{Project Administration}
	\subsection{Software Process and tools}
	UG02 decided to use the Agile software process to develop the Lunar Rover Mapping Robot. \\
	UG02 decided to use Overleaf and Texmaker software to create and edit LaTeX documents. \\
	UG02 decided to use Eclipe as the IDE to develop the software, because of its plug-in support and familiarity to the group's members. Eclipse is compatible with a LeJOS, Apache Ant, JUnit, and static code analysis plug-ins.
		
	\subsection{Management Roles}
	Six project management positions were defined such that each person would have a defined duty, and shadow position. The positions are as follows: \\
	\begin{tabular}{lll}
	\textbf{Title} & \textbf{Holder} & \textbf{Shadow} \\
	\textbf{Project Manager} & Brock Campbell & Andrew Graham \\
	\textbf{Design Manager} & Saxon Nelson-Milton & Alex Good \\
	\textbf{Documentation Manager} & Alex Good & Saxon Nelson-Milton \\
	\textbf{Test Manager} & Nathan Crowe & Mitchell Mickan \\
	\textbf{Quality Assurance} & Andrew Graham & Brock Campbell \\
	\textbf{Requirements Manager} & Mitchell Mickan & Nathan Crowe \\
	\end{tabular} \\ \\ \\
%	\vspace{0.5cm}
	Some of the management positions were given well defined responsibilities. In the next meeting, these should be further refined. \\ \\
	\textbf{Project Manager}
	\begin{itemize}
	\item Manages Schedule/Roadmap
	\item Risk Assessment
	\end{itemize}
	\textbf{Test Manager}
	\begin{itemize}
	\item Oversees tests to rigorously test the system
	\item Oversees JUnit testing code
	\end{itemize}
	\textbf{Quality Assurance}
	\begin{itemize}
	\item Appropriately designates pull requests
	\item Provides feedback pertaining to pull requests
	\end{itemize}
	\textbf{Requirements Manager}
	\begin{itemize}
	\item Oversees requirements
	\item Oversees requirement priority
	\item Oversees version management pertaining to requirements
	\end{itemize}
	 
\section{Adjournment}
	The next meeting time and location would be decided over 	UG02's Discord server. \\
	The meeting closed at 3:15pm.

\end{document}
