\documentclass{article}
\usepackage[utf8]{inputenc}
\begin{document}
\begin{center}    
{\huge Minutes of the Ninth Group Meeting \par}
\vspace{0.5cm}
{\large Group UG02 \par}
\vspace{0.5cm}
{\large Monday 8th October 2017 \par}
\vspace{0.5cm}
\end{center}

\begin{flushleft}
\begin{tabular}{ll}
{\bfseries Chair} & Alex Good \\
{\bfseries Minutes} & Andrew Graham \\
{\bfseries Members}
 & Brock Campbell \\
 & Mitchell Mickan \\
 & Jiashi (Josh) Song \\
{\bfseries Apologies}  & Saxon Nelson-Milton\\
\end{tabular}
\end{flushleft}

\section{Time and Place}
The {\itshape eighth} meeting in {\itshape week 10} for the Software Engineering Group Project Group was held in the {\bfseries Atrium of Ingkarni Wardli, with members joining a Discord discussion}, at {\bfseries 1:01pm on Monday 9th October 2017.} 

\section{Upcoming Assessments}
	\subsection{Ethics Presentation}
    It was noted that at the week 11 client meeting there would be a small presentation made by each group member about the ethical issues relating to a single character in the case study given to us. This study was distributed to the group via our Discord chat. 
    \subsection{Project Deliverables for Client Meeting}
It was noted that at the week 11 client meeting the SDD and code review were due and are to be completed by Saxon and Josh.
    \subsection{DTD -> Grid Map}
Our DTD to grid map code is almost ready to integrate, with Brock giving a quick explanation of how this was achieved.
    \subsection{Testing Discussion}
Given we do not have a testing manager, and the project is drawing to a close, our testing strategy was briefly mentioned. We will be adopting a very hands on approach to testing, with most of the functionality of the rover being physically assessed. It was noted that the testing review can be skipped in our group.
    \subsection{Final Presentation time}
The group voted on a final presentation time for week 13 and our decision was entered on the doodle poll from the SEP forums. Our final presentation will be on Monday in week 13 from 2-2:30pm.

\subsection{Final Remarks}
It was decided that for the next week, the goals were to complete the reviews, and to work through the issues on Github left over from our previous sprint.
     
\section{Adjournment}
	The next group meeting and will be held in the {\bf Atrium, Ingkarni Wardli} at {\bf 2:00pm on Monday 16th October 2017}.\newline
    The next client meeting and will be held in {\bf Room 462, Ingkarni Wardli} at {\bf 10:10am on Tuesday 10th October 2017}.\newline
The meeting closed at 1:32pm.
\end{document}
