 %%%%%% Weekly Meeting Agenda 08/08/2017
  \documentclass[11pt, a4paper]{article}
  \usepackage{times}
  \usepackage{ifthen}
  \usepackage{amsmath}
  \usepackage{amssymb}
  \usepackage{graphicx}
  \usepackage{setspace}

  %%% page parameters
  \oddsidemargin -0.5 cm
  \evensidemargin -0.5 cm
  \textwidth 15 cm
  \topmargin -1.2 cm
  \textheight 22 cm

  \renewcommand{\baselinestretch}{1.4}\normalsize
  \setlength{\parskip}{0pt}

  %% Meeting Details
  \newcommand{\meetingno}{ Sixth }
  \newcommand{\meetinglocation}{ Atrium, Ingkarni Wardli } %% Location
  \newcommand{\meetingdatetime}{ 2.00pm on Monday forth September 2017 } %% Date and time
  \newcommand{\meetingchair}{ Jiashi Song} %% Chair
  \newcommand{\meetingminutes}{ Mitchell } %% Minutes
  
    \begin{document}

  %%%mention the no, time, and venue of the meeting
  \noindent The {\bf \meetingno} Software Engineering Group Project weekly meeting will be held in {\bf \meetinglocation } at {\bf \meetingdatetime }.

  \vspace*{15pt}

  \begin{center}
  \huge \bf Agenda
  \end{center}

  %%%first, nominate a chair for the meeting. We suggest that each member at least has one chance as the chair.
  \section*{Chair: \meetingchair }
  \section*{Minutes: \meetingminutes }
  

  \vspace*{10pt}

  %%%if some students cannot make the meeting due to some reasons, their names should appear here.
  \section{Apologies}
  Saxon 

  %%%short presentation about the work of previous week or any milestone specified in the course.
  \section{Presentation}

  N/A

  %%%any schedules for this meeting should go next, each with a separate section.
  %%%for example, the first meeting is about requirement elicitation, like the following.
  \section{ Group issues }
   Nathan has dropped this course and left our group in last week, and Mitchell will take over the role of Test Manager .

  %%%more issues should make it like the above one.
  \section{Software Project Management Plan (SPMP)}
   The SPMP draft is due on Tuesday, and it seems like we have done pretty much so far. we still have time for integration or improvement. Does anyone have any problems or questions about SPMP. Feel free to discuss your own section or other member's section with team.
   
   \section{Milestone}
   We are required to prepare a milestone form that we will deliver for the first milestone in week 8. We need to consider available commitments to features in coming week.\newline
   We already have 3 features :\newline
   \begin{itemize}
   \item  basic movement (Forward, back, left right) (Done)
   \item  Reading Sensor Data (Touch Sensors so far)
   \item  Manual Control from UI (Not yet)
     \end{itemize} 
   what is the last feature we need to implement.(prototype A1 survey map ?)
   How should  we present the Milestone part in client meeting.
   
   \section{GUI}
   Any suggestion for current GUI design and layout.
   Josh already make the window and buttons bigger and make the Mode(Auto/Manual) more obvious, that's what David required. Also added save and open function into buttons, but currently we don't have any stored data.
   
   \subsection{Add survey map}
   Currently the plan is that GUI read data from XML, so do we need a new refresh screen button in multiple secs for that?
   
   \section{Survey map}
   Have we done A1 size Survey map so far?
   
   \section{Robot}
   What is the current status of the rover? What needs to be achieved before the first milestone?
   
  \section{Other issues}
  
  \subsection{Week 7 client meeting}
We are expected to present SPMP in the first 10-15 minutes, and the remaining of the session will continue with a regular client meeting.
\begin{itemize}
\item 
Any other items or questions should be discussed during client meetings?
  \end{itemize} 
  
  \subsection{Our goals}
  Make sure we can implement all features which are included in milestone 1 before next client meeting. 
  
  
%%%finally, specifies time of next meeting
  \vspace*{10pt}
  \noindent Note: Next meeting to be held on 11 September 2017.


  \end{document}
