\documentclass[a4paper]{article}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}


\title{Meeting 1 Agenda, 31/07/2017}
\date{}

\begin{document}
\maketitle

\begin{flushleft}

\section{Discussion points}
\begin{enumerate}
	\item How will we deal with latex and github ? 
	\begin{itemize}
		\item Latex - TexMaker suggested technology. Perhaps people can make documents in word/plain text and someone's role can be to make \LaTeX Docs. \textbf{Problem:} TexMaker makes a bunch of trash files. Perhaps each week should have a separate folder for manager docs?
		\item GitHub - Plan to use GitHub for everything
		\begin{itemize}
			\item Issue tracking (bugs etc.) with Issue tracker.
			\item Keeping track of user stories, work delegation (scrum board) on the Projects section of the repo.
			\item Proper branch usage (get someone else to review your pull requests to accept it. We can make this a role for a couple of people).
		\end{itemize}
	\end{itemize}
	
    \item How will we deal with timesheets ?
    \linebreak
    I believe Amali/David will put up a template to use. Otherwise, we can make an excel template in the repo.
    Each week, people can download the template, fill in their hours, and submit their timesheet to the repo. Thoughts?
    
    \item Is LeJOS on the uni computers ? 
    \linebreak
    \textbf{Action:} Ask Amali or David.
    
    \item What coding conventions shall we use ? 
    \linebreak
    Google Java Code Style? Oracle guide?
    
    \item Allocating project manager, and other positions. 
    \linebreak
    Need to figure out all roles we will need. Then we can allocate roles + shadow roles.
    
    \item What testing tool will we use ? 
\end{enumerate}


\section{Team Requirements and responsibilities (extracted from group project spec docs)}
Based on the docs, there are a bunch of requirements and responsibilities we need to look into.
\linebreak
Let's try and extract these requirements to make sure we don't miss anything important (such as saving docs to specific locations).

\end{flushleft}

\end{document}
