  %%%%%% Weekly Meeting Agenda 08/08/2017
  \documentclass[11pt, a4paper]{article}
  \usepackage{times}
  \usepackage{ifthen}
  \usepackage{amsmath}
  \usepackage{amssymb}
  \usepackage{graphicx}
  \usepackage{setspace}

  %%% page parameters
  \oddsidemargin -0.5 cm
  \evensidemargin -0.5 cm
  \textwidth 15 cm
  \topmargin -1.2 cm
  \textheight 22 cm

  \renewcommand{\baselinestretch}{1.4}\normalsize
  \setlength{\parskip}{0pt}

  %% Meeting Details
  \newcommand{\meetingno}{First}
  \newcommand{\meetinglocation}{Room 462, Ingkarni Wardli} %% Location
  \newcommand{\meetingdatetime}{10.10am on Tuesday 8th August 2017} %% Date and time
  \newcommand{\meetingchair}{ Brock Campbell } %% Chair
  \newcommand{\meetingminutes}{ Andrew Graham } 

  \begin{document}

  %%%mention the no, time, and venue of the meeting
  \noindent The {\em \meetingno} Software Engineering Group Project client meeting will be held in {\bf \meetinglocation } at {\bf \meetingdatetime }.

  \vspace*{15pt}

  \begin{center}
  \huge \bf Agenda
  \end{center}


\begin{flushleft}

  %%%first, nominate a chair for the meeting. We suggest that each member at least has one chance as the chair.
  \section*{Chair: \meetingchair }
  \section*{Minutes: \meetingminutes }
  

  \vspace*{10pt}

  %%%if some students cannot make the meeting due to some reasons, their names should appear here.
  \section{Apologies}
  N/A %% hopefully

  %%%short presentation about the work of previous week or any milestone specified in the course.
  \section{Presentation}
  N/A

  %%%any schedules for this meeting should go next, each with a separate section.
  %%%for example, the first meeting is about requirement elicitation, like the following.
  \section{Requirement Elicitation}

  %%%if there are more subissues, make them as subsections.
  \subsection{Elicit Lunar Rover Requirements}
  Functional requirements involve anything related to what quality and level of technology will be provided to carry out the mission. Clarification is required on the following points:

  \begin{enumerate}
  
  \item What sensors are available (infrared, colour) in the Lego Mindstorm EV3 Kit?
  \linebreak How can we know where the Lunar Rover is in the survey area without having a GPS?
  \linebreak How should we be "transmitting video" to an operator when there are no cameras? What information needs to be transmitted?
  
  \item "...demonstrate a prototype Lunar Rover that will travel 500 meters..." 
  \linebreak In this context, what is this 500 metre constraint applied to?
  
  \end{enumerate}
  
  
  \subsection{Elicit Mapping Requirements}
  Mapping requirements involve anything related to, or required for, constructing a survey map of the area the Rover lands in. Clarification is required on the following requirements: 
  
  \begin{enumerate}
  
  \item "...surveying area to search with a bounding box of 500 meters."
  \linebreak What shape is the bounding box?
  \linebreak How thick is the bounding box line (relative to regular lines)?
  \linebreak What colour are boundary lines?
  
  \item "Apollo 17 ... should have a weak radiation signature."
  \linebreak How is the radiation signature used? It it marked on the map?
  \linebreak Is there only one location where the Apollo 17 could be (parts haven't broken off)?
  \linebreak Is the mission accomplished after finding Apollo 17, or should surveying the area continue?
  
  \item "The map must be constructed in real-time and show significant features found."
  \linebreak What are significant features in this context?
  \linebreak How are these features differentiated from each other?
  \linebreak How is Apollo 17 differentiated from other surveyed objects?
  \linebreak How are dangerous obstacles differentiated from regular terrain?
  
  \item "The operator may designate no-go zones (NGZ)..."
  \linebreak How are these NGZ marked?
  \linebreak Does an operator define these on the survey map (rover avoids these areas), or are these locations marked physically in the survey area?
  
  \item "Sudden changes in the terrain gradient (i.e. craters) will be represented as a thick line."
  \linebreak Are all dangerous obstacles represented as thick lines?
  \linebreak Are thin lines used in the survey area? If so, what will these represent? How thick are thick lines compared to regular lines?
  
  \item "Lunar Rover must stay within the specified area unless directed otherwise."
  \linebreak Are we required to map areas outside of the survey area?
  
  \end{enumerate}
  
  
  \subsection{Elicit Mission Requirements}
  Mission requirements are related to anything that could comprimise the success of the mission, such as time constraits, locations for starting/ending a mission. Clarifications are required on the following points:
  
  \begin{enumerate}
  
  \item "Mostly concerned with the accuracy of the mapped representation.. vehicle shouldn't take forever!"
  \linebreak How is the accuracy of the mapped representation measured (map resolution)?
  \linebreak What is the slowest time acceptable for a Rover to map a survey area?
  
  \item "When the vehicle has accomplished the mission or prematurely stopped the survey, the vehicle must return to the Lunar Rover landing..."
  \linebreak Does the vehicle return autonomously or via manual control?
  \linebreak How close to the lunar rover landing?
  
  \end{enumerate}


  \subsection{Elicit Design Requirements}

  \begin{enumerate}
    \item "The operator has some form of visual surveillance of the vehicles operations."
    \linebreak What operations must be reported to the operator?
    
    \item What are the interface requirements for controlling the "Lunar Rover"?
    \linebreak What are the desirable features of the User Interface?
  \end{enumerate}


  \subsection{Elicit Uncategorized Requirements}
  Requirements that couldn't be categorized into the previous categories.
  
  \begin{enumerate}

  \item "There are many safety issues which must be addressed in this project."
  \linebreak What are these safety issues?
  
  \item What are the definition of DTD, CTO (Chief Technology Officer)?

  \item "To protect the expensive vehicle from harm as well as preserve the integrity of the site, the vehicle must not collide against an external object with any significant force."
  \linebreak What counts as significant force?

  \end{enumerate}

  %%%more issues should make it like the above one.
  \section{Other Issues}

\end{flushleft}
  %%%finally, specifies time of next meeting
  \vspace*{10pt}
  \noindent Note: Next meeting to be held on 15 August 2017.


  \end{document}
