\documentclass{article}
\usepackage[utf8]{inputenc}
\begin{document}
\begin{center}    
{\huge Minutes of the 8th Client Meeting \par}
\vspace{0.5cm}
{\large Group UG02 \par}
\vspace{0.5cm}
{\large Tuesday 10th October 2017 \par}
\vspace{0.5cm}
\end{center}

\begin{flushleft}
\begin{tabular}{ll}
{\bfseries Chair} & Alexander Good \\
{\bfseries Minutes} & Andrew Graham \\
{\bfseries Members} & Mitchell Mickan  \\
 & Jiashi Song \\ 

{\bfseries Apologies}  & Brock Campbell \\
& Saxon Nelson-Milton \\
\end{tabular}
\end{flushleft}

\section{Time and Place}
The {\itshape 8th} client meeting in {\itshape week 10} for the Software Engineering Group Project Group was held in the {\bfseries Ingkarnli Wardli 462}, at {\bfseries 10:10am on Tuesday 10th October 2017.} 

\section{Quorum Announcement}
    After a brief introduction by all asserting that all expected group members were present, it was announced that this meeting was to clarify any issues we might have regarding the project, and that there were no set presentations.. 

\section{Introduction}
  Since our last week meeting, it was noted that not much work has been done on the rover in the past week, aside from a few small bug fixes. 

\section{Milestone 2 Explanation}
	The goals we achieved in milestone 2 were explained to the client. Future plans to extend upon our current implementation were explained, with some explanation given to the way we were converting our DTD version of the map to our GUI display. Further work to complete includes fixing existing bugs in our repository, cleaning up the code for maintainability, and implementing no go zones within the GUI.

\section{Project Deliverables}
	It was noted that the code and SDD reviews had been completed and handed up that morning.

\section{Adjournment}	
    The next client meeting and will be held in {\bf Room 462, Ingkarni Wardli} where we will have our final rover presentation.
The meeting closed at 10:23am.

\end{document}