\documentclass{article}
\usepackage[utf8]{inputenc}
\begin{document}
\begin{center}    
{\huge Minutes of the 4th Client Meeting \par}
\vspace{0.5cm}
{\large Group UG02 \par}
\vspace{0.5cm}
{\large Tuesday 29st August 2017 \par}
\vspace{0.5cm}
\end{center}

\begin{flushleft}
\begin{tabular}{ll}
{\bfseries Chair} & Nathan Crowe \\
{\bfseries Minutes} & Jiashi Song \\
{\bfseries Members} & Andrew Graham  \\
 & Alexander Good \\
 & Mitchell Mickan \\
 & Saxon Nelson-Milton \\
 & Brock Campbell \\
{\bfseries Apologies} & None\\
\end{tabular}
\end{flushleft}

\section{Time and Place}
The {\itshape 4th} client meeting in {\itshape week 6} for the Software Engineering Group Project Group was held in the {\bfseries Ingkarnli Wardli 462}, at {\bfseries 10:10am on Tuesday 29st August 2017.} 

\section{Quorum Announcement}
	After a brief introduction by the client, it was announced that the first 15 minutes would be dedicated to presenting GUI prototype and basic movement demo .
    
\section{Summary of Previous Meeting}
 	Not Applicable - This was not discussed.

\section{GUI prototype}
Josh showed GUI draft ,which met basic requires so far but some function should be implemented by the next meeting.
\begin{flushleft}
\textbf{Q:}Do we need the function to get status from Rover (show status button)?
\linebreak\textbf{A:} It was a nice try, team need to know how GUI obtains values from  sensors in data structure .
\linebreak\textbf{Q:} Do we need to resize the window or just use absolute layout ?
\linebreak\textbf{A:} It is not need to implemented now before completed survey map .
\end{flushleft}
\subsection{Feedback}
\begin{enumerate}
\item Change the button's size , which should be similar to Save/folder button.  
\item Two modes distinction should be more obvious ; Current mode should be evident by operator .
\end{enumerate}

\section{Survey map}
Andrew presented the survey map . Most of details were implemented and met the requires ,including crater,object, crash landing trails ,footprints ,rover trails and Apollo 17. 
\subsection{Feedback}
\begin{enumerate}
\item Modify the landing site/trails .
\item The request of survey map is A1 size .
\item Final version should be added to GUI , all color should be reasonable allocated .
\end{enumerate}

\section{Basic movement demo}
Physical demonstration of the rover was good .Successfully demonstrated forward ,backward, right/left turns and stop .
\subsection{Feedback}
\begin{enumerate}
\item Test the hardware, including wheels , bumpers and sensors.
\item Rover moving debugging ,especially stop and left/right turns.
\item Bumper sensor issues and wheels issues should be improved .
\item Demonstrate the rover moving at a high speed .
\item Recommend JavaScript programming .  
\end{enumerate}

\section{SRS review}
Mitchell will upload his review video to YouTube.

\section{Next Meeting Deliverables}
It was discussed that Software Project Management Plan should be implemented before next client meeting .

\section{Adjournment}
	The next group meeting and will be held in the {\bf Atrium, Ingkarni Wardli} at {\bf 2:00pm on Monday Fourth of September  2017}.
    \newline
    The next client meeting and will be held in {\bf Room 462, Ingkarni Wardli} at {\bf 10:10am on Tuesday fifth of September 2017}.
The meeting closed at 10:38am.







\end{document}