\documentclass{article}
\usepackage[utf8]{inputenc}
\begin{document}
\begin{center}    
{\huge Minutes of the Third Client Meeting \par}
\vspace{0.5cm}
{\large Group UG02 \par}
\vspace{0.5cm}
{\large Tuesday 22nd August 2017 \par}
\vspace{0.5cm}
\end{center}

\begin{flushleft}
\begin{tabular}{ll}
{\bfseries Chair} & Andrew Graham \\
{\bfseries Minutes} & Brock Campbell \\
{\bfseries Members} & Nathan Crowe \\
 & Alexander Good \\
 & Mitchell Mickan \\
 & Saxon Nelson-Milton \\
 & Jiashi (Josh) Song \\
{\bfseries Apologies} & None\\
\end{tabular}
\end{flushleft}

\section{Time and Place}
The {\itshape third} client meeting in {\itshape week 5} for the Software Engineering Group Project Group was held in the {\bfseries Ingkarnli Wardli 462}, at {\bfseries 10:10am on Tuesday 22nd August 2017.} 

\section{Quorum Announcement}
    After a brief introduction by the client, it was announced that the first 10 minutes would be dedicated to discussing the Software Requirements Specification document.
    
\section{Summary of Previous Meeting}
    Not Applicable - This was not discussed.
    
\section{Software Requirements Specification Presentation}
The SRS was discussed briefly with each section and their purpose being outlined, after which a series of clarification questions were asked by the client.
\begin{flushleft}
\textbf{Q:} What is the purpose of the Quality section?
\linebreak\textbf{A:} The description of modular, extendable software being produced, such that other companies may use the rover system after the initial survey task.
\linebreak\textbf{Q:} Do all requirements have dependencies?
\linebreak\textbf{A:} Sensors do not have dependencies, since their functionality is independent of all other requirements, and they are required for more complicated requirements.
\linebreak\linebreak
There were a set of suggestions the client had to improve the readibility of the document.
\linebreak\textbf{Suggestion:} Create a table to label/link stimuli/response patterns with their functional requirement definition (ease of understanding).
\linebreak\textbf{Suggestion:} Include in section 1 descriptions of every other section and what their purposes are.
\linebreak\textbf{Suggestion:} Add a section outlining system requirements - which OS is being used, compute system, the EV3 Brick, expected amount of memory used etc.


\section{Requirements Discussion}
Further discussion was required on the design of the physical survey map.
\linebreak\textbf{Q:} Are the colours up to us for significant features or are there limitations?
\linebreak\textbf{A:} The only limitation is that the craters are represented as thick black lines. All other significant features are up to us.
\end{flushleft}
\section{Next Meeting Deliverables}
It was discussed that there should be a set of deliverables for the next client meeting to showcase our progress.
\begin{enumerate}
\item System architecture design: It would be useful to showcase a basic architecture design to the client by next week to outline which areas interact with each other.
\item Basic prototype movement and touch sensor functionality: After the first sprint (Expected completion: Monday 28th), a working prototype should be produced with basic movement and touch sensor functionality.
\item User Interface:
There is a prototype user interface already produced by Josh to be showcased next week.
\end{enumerate}
\section{Adjournment}
    The next group meeting and will be held in the {\bf Atrium, Ingkarni Wardli} at {\bf 2:00pm on Monday 28th August 2017}.\newline
    The next client meeting and will be held in {\bf Room 462, Ingkarni Wardli} at {\bf 10:10am on Tuesday 29th August 2017}.\newline
The meeting closed at 10:34am.
\end{document}