\documentclass{article}
\usepackage[utf8]{inputenc}
\begin{document}
\begin{center}    
{\huge Minutes of the 7th Client Meeting \par}
\vspace{0.5cm}
{\large Group UG02 \par}
\vspace{0.5cm}
{\large Tuesday 3rd October 2017 \par}
\vspace{0.5cm}
\end{center}

\begin{flushleft}
\begin{tabular}{ll}
{\bfseries Chair} & Alexander Good \\
{\bfseries Minutes} & Brock Campbell \\
{\bfseries Members} & Mitchell Mickan  \\
 & Jiashi Song \\ 
 & Andrew Graham \\
 & Saxon Nelson-Milton \\
{\bfseries Apologies}
\end{tabular}
\end{flushleft}

\section{Time and Place}
The {\itshape 7th} client meeting in {\itshape week 9} for the Software Engineering Group Project Group was held in the {\bfseries Ingkarnli Wardli 462}, at {\bfseries 10:10am on Tuesday 3rd October 2017.} 

\section{Quorum Announcement}
    After a brief introduction by all asserting that all expected group members were present, it was announced that this meeting was to present the System Design Document (SDD) and the Milestone 2 Presentation.

\section{Introduction}
  Since our last week meeting, a lot of work went into the rover to complete the second milestone.

\section{SDD presentation}
The presentation went smoothly, with some questions by the team, and feedback from the client.
\begin{flushleft}
{\bfseries Client Q:} Explain the system architecture better?\linebreak
{\bfseries A:} Saxon explained the reasoning behind the basic architecture diagram.\linebreak
{\bfseries Client Q:} Why group classes into separate diagrams?\linebreak
{\bfseries A:} There was too much detail in one graph.\linebreak
{\bfseries Saxon Q:} How to go from architecture to classes?\linebreak
{\bfseries A:} Go into each omponent and have class diagram for each component/module. Abstract many complex things from class diagrams to simplify. Explain why each component is needed and satisfies components.\linebreak
{\bfseries Client Q:} Why use the basic diagram over the advanced diagram?\linebreak
{\bfseries A:} Saxon explained the use of less complex components in the basic diagram. \linebreak \linebreak

{\bfseries Feedback:} Put more about design rationale (what design pattern? MVC? EDC?)\linebreak
{\bfseries Feedback:} Add priority diagram for behaviours\linebreak
{\bfseries Feedback:} Some names of described elements in the system don't match up with the diagrams.\linebreak
{\bfseries Feedback:} Document behaviour -> state diagrams and use-case diagram (show how it works when running).\linebreak

\end{flushleft}
	
\section{Milestone 2 presentation}
\begin{flushleft}
All goals were achieved and documented to have been achieved during the milestone presentation.
\end{flushleft}

\section{Adjournment}	
    The next client meeting and will be held in {\bf Room 462, Ingkarni Wardli}, 10th October 2017.
The meeting closed at 10:23am.

\end{document}